Methods for Feature Learning and Extraction

### 2017-05-01 paper/tex/Paper.tex
Updates

@@

Feature learning is widely regarded as a fundamental basis for many modern machine learning algorithms, specifically those classified under unsupervised learning. Its applications span a wide variety of fields, ranging from determining the connectedness of airports to classifying an apartment?s location based solely on a few properties. In particular, researchers have focused on image recognition; they are intrigued that the human brain can easily process and interpret images, yet even extremely powerful computers struggle to do the same. It is only logical then that researchers have turned to the human brain for inspiration and have attempted to mimic the visual cortex?s operations in code. Several methods and algorithms have developed over the years with some remarkable success, despite their drawbacks

In general, these algorithms follow a similar structure in terms of their derivation and operation. The basic equation that they try to solve is 
\begin{align*}
    X = W Z
\end{align*}
where  is the code matrix that represents a decomposed version of the input set and  is the weight matrix, which varies based on the output we are trying to derive. From here, the models diverge by placing different constraints on the input, the code matrix, or the weight matrix. In some cases, the constraint is enforced by transforming the input to satisfy it. A reconstruction error is then defined and minimized to determine the best code matrix for the model. Some methods also outline a method for preprocessing the input, which helps increase the accuracy of the trained model.

@@

In their paper on sparse coding, Bruno Olshausen and David Field utilize the above steps to recreate the visual cortex?s functionality to improve image recognition. From their perspective, the brain removes redundancy from the information it receives from the photoreceptors and represents the image as a collection of independent events (Olshausen 3311). Previous research in sparse coding focused on 2-dimensional redundancy reduction, which completely omits curves and other higher dimensional collections seen in natural images. To increase the accuracy of existing sparse coding algorithms, Olshausen and Field explore the creation of a linear strategy that can reduce higher order redundancy.

@@

>>>>

\usepackage{textcomp}

@@

Feature learning is widely regarded as a fundamental basis for many modern machine learning algorithms, specifically those classified under unsupervised learning. Its applications span a wide variety of fields, ranging from determining the connectedness of airports to classifying an apartment's location based solely on a few properties. In particular, researchers have focused on image recognition; they are intrigued that the human brain can easily process and interpret images, yet even extremely powerful computers struggle to do the same. It is only logical then that researchers have turned to the human brain for inspiration and have attempted to mimic the visual cortex's operations in code. Several methods and algorithms have developed over the years with some remarkable success, despite their drawbacks

In general, these algorithms follow a similar structure in terms of their derivation and operation. The basic equation that they try to solve is:
\begin{align*}
    X = W Z
\end{align*}
where  is the code matrix that represents a decomposed version of the input set and  is the weight matrix, which varies based on the output we are trying to derive. From here, the models diverge by placing different constraints on the input, the code matrix, or the weight matrix. In some cases, the constraint is enforced by transforming the input to satisfy it. A reconstruction error is then defined and minimized to determine the best code matrix for the model. Some methods also outline a method for preprocessing the input, which helps increase the accuracy of the trained model.

@@

In their paper on sparse coding, Bruno Olshausen and David Field utilize the above steps to recreate the visual cortex's functionality to improve image recognition. From their perspective, the brain removes redundancy from the information it receives from the photoreceptors and represents the image as a collection of independent events (Olshausen 3311). Previous research in sparse coding focused on 2-dimensional redundancy reduction, which completely omits curves and other higher dimensional collections seen in natural images. To increase the accuracy of existing sparse coding algorithms, Olshausen and Field explore the creation of a linear strategy that can reduce higher order redundancy.

@@

\section {Stacked Denoising Autoencoders}
